\plaintitle

### 2016-09-13 drafts/labor/abstract.tex
piecework_lit should be kind of done
lots of changes all over the place

\makeatletter
\def\blx@maxline{77}
\makeatother
% \zexternaldocument*{complexity}

@@

\begin{abstract}
Networked computation is enabling the rise of
crowdwork,
gig work, and
other forms of on--demand labor.
A large and growing body of scholarship has sought to predict
the socio--technical outcomes of this shift, especially
\nameref{sec:complexity} how complex and interdependent crowdwork's tasks can be,
\nameref{sec:decomposition} how thinly crowdwork can be sliced and modularized, and
\nameref{sec:relationships} what the collective outcomes will be for crowdworkers.
In this paper, we look to the historical scholarship on piecework
--- a strikingly similar trend of
work decomposition,
distribution, and
payment that was popular at the turn of the \nth{20} century ---
to understand how these questions might play out with modern crowdwork.
To do so, we identify the mechanisms that limited piecework historically, and
identify whether crowdwork faces the same mechanism limits or might differentiate itself.

% We consider the aforementioned open questions in the body of research on crowdwork
% under the following framework:
% \begin{inlinelist}
% \item we look to the familiar literature in human computation;
%       then
% \item we investigate the scholarship on piecework;
% \item we identify what (if anything) has changed in crowdwork to differentiate it from piecework;
%       and finally
% \item we attempt to provide a concise prediction on these open questions,
%       informed by piecework's insights.
% \end{inlinelist}

% With growing attention toward on--demand labor
% --- ranging from the ``sharing economy'' to information work ---
% scholars have made connections to various frameworks 
% and mechanisms such as worker advocacy, empowerment, and Taylorism,
% to make sense of our observations of
% on--demand work and the workers that power this movement.
% We argue that the literature surrounding ``piecework''
% informs and even predicts both the contributions
% that have been made toward the development of on--demand labor and crowd work
% as well as the fallout among workers and researchers
% with regard to the disillusionment and alienation of work.

% After evaluating this framing
% through a series of case studies,
% we look to the future
% to identify worthwhile questions and
% points of inquiry, such as the movement toward factories,
% that researchers in social computing should consider
% as we attempt to anticipate and perhaps shape the future of work.
\end{abstract}

% \onlyinsubfile{
% \clearpage
% \subfile{cases}
% }

\end{document}

>>>>

\makeatletter
\def\blx@maxline{77}
\makeatother

@@

\begin{abstract}
The Internet is enabling the rise of
crowd work,
gig work, and
other forms of on--demand labor.
A large and growing body of scholarship has sought to predict
the socio--technical outcomes of this shift, especially along three threads: %. This question has been dominated by three threads:
\begin{inlinelist}
\item \nameref{sec:complexity};
\item \nameref{sec:decomposition}; and
\item \nameref{sec:relationships}.
\end{inlinelist}
In this paper, we look to the historical scholarship on piecework
--- a similar trend of
work decomposition,
distribution, and
payment that was popular at the turn of the \nth{20} century ---
to understand how these questions might play out with modern crowd work.
To do so, we identify the mechanisms that limited piecework historically, and
identify whether crowd work faces the same mechanism limits or might differentiate itself.
This approach to understanding crowd work provides additional theoretical framing
to make sense of a topic with which researchers continue to struggle to understand.
\end{abstract}
\end{document}

### 2016-09-13 drafts/labor/cases.tex
lots of changes all over the place

We look at lots of papers that use the term ``crowdsourcing'' or ``crowdwork''
in the abstracts and titles of their papers%
, especially the papers that we cited earlier, to try
to answer the questions that we posed in the introduction.
Then we look to the piecework literature to see whether and to what extent
piecework answers the questions we, crowdsourcing researchers, have asked.
We then see whether and how crowdsourcing as we know it has differed from piecework%
, and how that affects the predictions and conclusions made in the piecework literature.
% look at review papers

% what's the methodology?
% make piecework literature much clearer about argument
% make headers clearer to signal what i'm doing here.

@@

%                        _ _      _ 
%  _ __   __ _ _ __ __ _| | | ___| |
% | '_ \ / _` | '__/ _` | | |/ _ \ |
% | |_) | (_| | | | (_| | | |  __/ |
% | .__/ \__,_|_|  \__,_|_|_|\___|_|
% |_|

@@

\subsubsection{So how does this affect crowdwork?}
The work we've seen so far 
\begin{itemize}
  \item worst case: assembling iPhones (extant)
  \item average case: railroad workers and assembly lines
  \item high (complexity) case: 
\end{itemize}

@@

    Understanding workers' motivations given these conditions has thus become a goal for some researchers
    \cite{whyWouldAnyoneBrewer}.
    \citeauthor{Sun20111033} conclude that
    ``\dots~solvers participate in online tasks
    not only for money
    but also for enjoyment
    or the sense of self--worth''
    \cite{Sun20111033}.
    This might have rung true in \citeyear{Sun20111033}%
,     and certainly corroborates \citeauthor{Ross}'s findings after investigating
    ``who are the crowdworkers''%
,     but as \citeauthor{whoareNOTtheTurkers} points out
    ``we [have since] learned that most tasks on AMT are done by a small group of professional Turkers\dots''
    \cite{Ross,whoareNOTtheTurkers}.

@@

    \subsubsection{Variable quality work}
    Researchers have struggled with what we might generously call work of ``variable quality''
    along two dimensions.
    The first, to use the characterization of one of these contributions, we can call
    ``understanding malicious behavior''
    \cite{MaliciousCrowdworkersGadiraju}.
    While some work has cast workers as ``malicious'' or at least adversarial parties%
,     the evidence thus far suggests that
    workers behave in unexpected ways as they attempt to assert some control over their interaction with the system
    (a topic of discussion to which we'll return later)
    \cite{uberAlgorithm}.
    The second dimension of research in this space generally attempts
    to eke out the highest quality work possible from workers
    given the apparent difficulty in predicting work outcomes
    \cite{embracingErrorKrishna}.

>>>>

We look at lots of papers that use the term ``crowdsourcing'' or ``crowd work''
in the abstracts and titles of their papers%
, especially the papers that we cited earlier, to try
to answer the questions that we posed in the introduction.
Then we look to the piecework literature to see whether and to what extent
piecework answers the questions we, crowdsourcing researchers, have asked.
We then see whether and how crowdsourcing as we know it has differed from piecework%
, and how that affects the predictions and conclusions made in the piecework literature.

@@

@@

\subsubsection{So how does this affect crowd work?}
The work we've seen so far 
\begin{itemize}
  \item worst case: assembling iPhones (extant)
  \item average case: railroad workers and assembly lines
  \item high (complexity) case: 
\end{itemize}

@@

    Understanding workers' motivations given these conditions has thus become a goal for some researchers
    \cite{whyWouldAnyoneBrewer}.
    \citeauthor{Sun20111033} conclude that
    ``\dots~solvers participate in online tasks
    not only for money
    but also for enjoyment
    or the sense of self--worth''
    \cite{Sun20111033}.
    This might have rung true in \citeyear{Sun20111033}%
,     and certainly corroborates \citeauthor{Ross}'s findings after investigating
    ``who are the crowd workers''%
,     but as \citeauthor{whoareNOTtheTurkers} points out
    ``we [have since] learned that most tasks on AMT are done by a small group of professional Turkers\dots''
    \cite{Ross,whoareNOTtheTurkers}.

@@

    \subsubsection{Variable quality work}
    Researchers have struggled with what we might generously call work of ``variable quality''
    along two dimensions.
    The first, to use the characterization of one of these contributions, we can call
    ``understanding malicious behavior''
    \cite{MaliciouscrowdworkersGadiraju}.
    While some work has cast workers as ``malicious'' or at least adversarial parties%
,     the evidence thus far suggests that
    workers behave in unexpected ways as they attempt to assert some control over their interaction with the system
    (a topic of discussion to which we'll return later)
    \cite{uberAlgorithm}.
    The second dimension of research in this space generally attempts
    to eke out the highest quality work possible from workers
    given the apparent difficulty in predicting work outcomes
    \cite{embracingErrorKrishna}.

### 2016-09-13 drafts/labor/complexity.tex
lots of changes all over the place

% \renewcommand{\topic}[1]{#1}
\subsubsection[finding crowdwork's limits]{Achieving greater complexity}\label{sec:complexity}
\subsubsubsection{\crowdworkpers}
\topic{Crowdsourcing research has spent the better part of a decade attempting
to prove the viability of crowdsourcing in increasingly complex work.}  % this is my topic sentence.
\citeauthor{crowdForgeKittur}
map the discussion toward this goal in their work on
crowdsourcing complex work
\cite{crowdForgeKittur}.
The broader body of work has varied significantly in type
--- providing conversational assistants%
, interpreting medical data, and
telling coherent and compelling stories%
, to name a few examples
\cite{Lasecki:2013:CCC:2501988.2502057,mavandadi2012distributed,KimStoria}.

\topic{This body of research has involved similar approaches to problems%
, often involving insights made in Computer Science and applied to human work--flows.}
The crowdwork literature typically identifies target milestones in CS
that have presented significant challenges for researchers%
, leverages some of the approaches and insights that Computer Science researchers have already made
(for example, MapReduce in the case of \citeauthor{crowdForgeKittur}'s \textit{CrowdForge})%
, and arranges humans as computational black boxes within those approaches and processes
\cite[][and others]{crowdForgeKittur,foundry}.
This approach has proven a compelling one because
it leverages the in--built advantages that technology and digital media afford.
\textit{Foundry}'s tools for managing and arranging expert groups into a cohort
allow researchers to convincingly argue that expert teams can be rapidly formed%
, just like non--expert teams
\cite{foundry}.

@@

\topic{This isn't to say that complex work is outside of the realm of piecework;
indeed, we've discussed complex applications of crowdwork already.}
As \citeauthor{hart2013rise} described,
the 1930s saw a flourishing of clever piecework job design out of necessity
due to the fact that it was infeasible to provide new workers with
the comprehensive education that was familiar to men
\cite{hart2013rise}.
This constraint led to much more tightly scoped work, and
(perhaps surprisingly at the time) more efficient allocations of workers,
who could now specialize in extremely narrowly defined roles.
The same could be said of Airy and his \textit{computers}
--- young boys whose preparations consisted principally of
a relatively specific mathematics curriculum
\cite{grier2013computers}.

@@

\subsubsubsection{\implication}
\topic{The piecework literature gives us a template for pushing the boundaries of complexity in piecework, but
it also signals some of the ultimate limitations of crowdwork and piecework in general.}
While the threshold preventing task requesters from utilizing piecework
has dropped thanks to affordances of the Internet, the ceiling on task complexity hasn't moved significantly.
If we're to make use of \citeauthor{Brown01041990}'s prescriptions,
we would benefit from finding ways to decompose varied tasks into homogeneous microtasks.

We should also consider exploring the limitations that algorithmic management bring along more carefully.
While research has touched on this subject, we've yet to make out the bigger picture of this theme
\cite{uberAlgorithm}.
If we can resolve the tension between workers and perilously antagonistic managers, as \citeauthor{10.2307/2118435} suggest,
then we may be able to break a toxic cycle of mistrustful requesters \cite[for example][]{MaliciousCrowdworkersGadiraju}
and develop more considerate platforms as \citeauthor{takingAHITMcInnis} advocate
\cite{takingAHITMcInnis}.

Finally, and perhaps most importantly,
we need to replicate the success of narrowly slicing education and training for expert work
as \citeauthor{hart2013rise} and \citeauthor{grier2013computers} described in their piecework examples
\cite{hart2013rise,grier2013computers}.
That is, we need to identify new ways to train crowdworkers for uniquely narrowly defined work.
To some extent, an argument can be made that
MOOCs and other online education resources
provide crowdworkers with the resources that they need, but 
it remains to be seen whether that work will be appropriately valued, let alone
properly interpreted by task solicitors
\cite{aguaded2013mooc}.
If we can overcome this obstacle,
we might be able to empower crowdworkers to do complex work such as engineering and metalworking,
rather than doom them to match girl reputations:
``brash, irregular, immoral, and uneducated''
\cite{10.2307/3827491}.

% \topic{Crowdsourcing falters when the routinization of complex work becomes too difficult.}
% \ali{Something about complexity being difficult to make routine when
% there are lots of little, varied, unpredictable tasks (nod to \citeauthor{Brown01041990})}

\onlyinsubfile{
  \balance{}
  \printbibliography
  % \clearpage
  \nobalance{}
  }

%   \endnotetext{
% %     \topic{We summarize the work discussed so far in this way:
% %     researchers of crowdsourcing and on--demand labor in general
% %     have attempted to find the characteristics which
% %     enable and stymie successful applications of this form of work%
% % ,     and how to get past or around these boundaries.}
% %     Whether this work has focused on the self (as in the case of ``selfsourcing'')
% %     or on others (as in \textit{CrowdForge} and \textit{Foundry})%
% % ,     crowdsourcing literature has generally studied the constituent work
% %     and attempted either to work around
% %     or indeed with
% %     the limitations of crowdwork to accomplish a difficult task
% %     \cite{selfsourcingTeevan2014,selfsourcingTeevan2016,crowdForgeKittur,foundry}.

% %     Crowdforge, turkomatic, others talk about limiting factors; bring them up

%       % Talked to someone about this section and got some feedback\dots
%       % \begin{enumerate}
%       %   \item Explain what ``clever arrangement of work'' in the first paragraph means
%       %         (should be simple; Find--Fix--Verify is the \textit{sort} of thing I mean);
%       %   \item I should make the ``selfsourcing'' stuff clearer for people unfamiliar with it
%       %         (maybe even to justify its placement here); and
%       %   \item I should break up \citeauthor{10.2307/23702539} \& \citeauthor{Brown01041990}
%       %         to make the historical stuff on piecework
%       %         directly speak to the three previous paragraphs.
%       %   \item (Maybe?) summarize the piecework stuff
%       %         (the last paragraph approaches that, but more could be done).
%       % \end{enumerate}
%       % Thoughts on this?

% %   \citeauthor{10.2307/23702539} also argues that
% %   a significant obstacle to the introduction of piecework in railroad shops was
% %   the resistance of workers
% %   (the other being the resistance of management (for different and varying reasons)).
% %   In the cases of online platforms like AMT and digitally mediated platforms like Uber%
% % ,   where in both cases workers rarely
% %   if ever
% %   interact face--to--face and
% %   opportunities for coordination and collective action are severely limited%
% % ,   we should expect to see
% %   the challenges stymieing collective action
% %   that we see in \citeauthor{dynamo} and elsewhere
% %   \cite{10.2307/23702539,dynamo}.
% }

>>>>

% \renewcommand{\topic}[1]{#1}
\subsubsection[finding crowd work's limits]{Achieving greater complexity}\label{sec:complexity}
\subsubsubsection{\crowdworkpers}
\topic{Crowdsourcing research has spent the better part of a decade attempting
to prove the viability of crowdsourcing in increasingly complex work.}  % this is my topic sentence.
\citeauthor{crowdForgeKittur}
map the discussion toward this goal in their work on
crowdsourcing complex work
\cite{crowdForgeKittur}.
The broader body of work has varied significantly in type
--- providing conversational assistants%
, interpreting medical data, and
telling coherent and compelling stories%
, to name a few examples
\cite{Lasecki:2013:CCC:2501988.2502057,mavandadi2012distributed,KimStoria}.

\topic{This body of research has involved similar approaches to problems%
, often involving insights made in Computer Science and applied to human work--flows.}
The crowd work literature typically identifies target milestones in CS
that have presented significant challenges for researchers%
, leverages some of the approaches and insights that Computer Science researchers have already made
(for example, MapReduce in the case of \citeauthor{crowdForgeKittur}'s \textit{CrowdForge})%
, and arranges humans as computational black boxes within those approaches and processes
\cite[][and others]{crowdForgeKittur,foundry}.
This approach has proven a compelling one because
it leverages the in--built advantages that technology and digital media afford.
\textit{Foundry}'s tools for managing and arranging expert groups into a cohort
allow researchers to convincingly argue that expert teams can be rapidly formed%
, just like non--expert teams
\cite{foundry}.

@@

\topic{This isn't to say that complex work is outside of the realm of piecework;
indeed, we've discussed complex applications of crowd work already.}
As \citeauthor{hart2013rise} described,
the 1930s saw a flourishing of clever piecework job design out of necessity
due to the fact that it was infeasible to provide new workers with
the comprehensive education that was familiar to men
\cite{hart2013rise}.
This constraint led to much more tightly scoped work, and
(perhaps surprisingly at the time) more efficient allocations of workers,
who could now specialize in extremely narrowly defined roles.
The same could be said of Airy and his \textit{computers}
--- young boys whose preparations consisted principally of
a relatively specific mathematics curriculum
\cite{grier2013computers}.

@@

\subsubsubsection{\implication}
\topic{The piecework literature gives us a template for pushing the boundaries of complexity in piecework, but
it also signals some of the ultimate limitations of crowd work and piecework in general.}
While the threshold preventing task requesters from utilizing piecework
has dropped thanks to affordances of the Internet, the ceiling on task complexity hasn't moved significantly.
If we're to make use of \citeauthor{Brown01041990}'s prescriptions,
we would benefit from finding ways to decompose varied tasks into homogeneous microtasks.

We should also consider exploring the limitations that algorithmic management bring along more carefully.
While research has touched on this subject, we've yet to make out the bigger picture of this theme
\cite{uberAlgorithm}.
If we can resolve the tension between workers and perilously antagonistic managers, as \citeauthor{10.2307/2118435} suggest,
then we may be able to break a toxic cycle of mistrustful requesters \cite[for example][]{MaliciouscrowdworkersGadiraju}
and develop more considerate platforms as \citeauthor{takingAHITMcInnis} advocate
\cite{takingAHITMcInnis}.

Finally, and perhaps most importantly,
we need to replicate the success of narrowly slicing education and training for expert work
as \citeauthor{hart2013rise} and \citeauthor{grier2013computers} described in their piecework examples
\cite{hart2013rise,grier2013computers}.
That is, we need to identify new ways to train crowd workers for uniquely narrowly defined work.
To some extent, an argument can be made that
MOOCs and other online education resources
provide crowd workers with the resources that they need, but 
it remains to be seen whether that work will be appropriately valued, let alone
properly interpreted by task solicitors
\cite{aguaded2013mooc}.
If we can overcome this obstacle,
we might be able to empower crowd workers to do complex work such as engineering and metalworking,
rather than doom them to match girl reputations:
``brash, irregular, immoral, and uneducated''
\cite{10.2307/3827491}.

\onlyinsubfile{
  \printbibliography
  }

### 2016-09-13 drafts/labor/decomposition.tex
lots of changes all over the place

@@

\subsubsubsection{\whatchanged}
 \topic{A number of factors in crowdwork are different from piecework,
 chief among them being the relative ease with which
 the metaphorical ``assembly line'' can be changed.}
 Computers make it possible to switch from one task to another
unlike any arbitrary manufacturing factory possibly could;
a worker could do any number of
different \textit{types} of tasks in the span of just a few minutes
\cite{delayAndOrderLasecki}.
This has spurred an entire body of work investigating the effects of
ordering,
pacing,
interruptions, and
other factors in piecework that would have been
all but impossible to measure consistently as few as 20 years ago
\cite{cheng2015break,measuringCrowdsourcingCheng,embracingErrorKrishna}.

@@

Rather than fall into the trap that \citeauthor{irani2015cultural} warns of,
--- one which where crowdworkers are rendered as
``modular, protocol--defined computational services'' ---
we may yield better results from crowdwork if we think of workers as similar to
specialized, repurposable tools
\cite{irani2015cultural}.
\ali{feeling meh about this argument\dots}

@@

\subsubsubsection{\implication}
Crowdwork research today is on the right track to investigate pipelining and meta--task design.
That is, investigating better work discovery methods, producing tools for workers to make more informed decisions
\cite[see, for example,][]{turkopticon}.
It's not clear how much benefit there is in the further decomposition of work,
given that we've hit bottlenecks with the cognitive stresses of switching between tasks
as \citeauthor{delayAndOrderLasecki} highlight
\cite{delayAndOrderLasecki}.

\onlyinsubfile{
  \balance{}
  \printbibliography

  % \clearpage
  % \nobalance{}
  }
%   \endnotetext{
% %     \section{Slicing notes}
% %     The finding here is that
% %     crowdwork can be more carefully micro--managed than piecework could be%
% % ,     and that this is a double--edged sword:
% %     we can effectively give feedback to workers on everything they do%
% % ,     but this is emboldening us to try to
% %     over--manage workers just as piecework tried to do.

% %     My goal for this section is to make two points:
% %     \begin{enumerate}
% %       \item show how this is related to the assembly line and scientific management%
% % ,             and how piecework literature tried to measure everything%
% % ,             but found it untenable given the extra equipment that was necessary
% %             (but generally which didn't exist)
% %             to track every movement and action that workers took.
% %       \item show how this work was enabled by the ``verifiability'' of work output(?)
% %     \end{enumerate}

%     % \ali{i don't like this section \textit{here}, but i like it in general. what do?}

%   }

>>>>

Earlier we discussed \citeauthor{cheng2015break}'s work
measuring the impact that interruption has on worker performance
\cite{cheng2015break}.
This work illustrates a broader sentiment in
both the study and practice
of crowd work, that microtasks should be designed resiliently against the variability of workers%
, fully exploiting the abstracted nature of each piece of work
\cite{interruptionIqbal,delayAndOrderLasecki,vaish2014low}.
That is to say, micro--tasks should be designed such that a single worker's poor performance%
, or a good worker's sudden departure%
, does not significantly impact the agenda of the work as a whole.
While \citeauthor{cheng2015break} found costs with breaking tasks into smaller components
in the form of higher cumulative time to complete
(albeit much shorter real time to complete, owing to parallelization)%
, \citeauthor{delayAndOrderLasecki} found that at least \textit{some} performance can be recouped by stringing 
similar tasks together
\cite[respectively]{cheng2015break,delayAndOrderLasecki}.

@@

\subsubsubsection{\whatchanged}
 \topic{A number of factors in crowd work are different from piecework,
 chief among them being the relative ease with which
 the metaphorical ``assembly line'' can be changed.}
 Computers make it possible to switch from one task to another
unlike any arbitrary manufacturing factory possibly could;
a worker could do any number of
different \textit{types} of tasks in the span of just a few minutes,
driven in particular by the power \citeauthor{lessig2006code} points to ---
that system--designers can share, modify, and instantiate environments
like sites of labor in a few lines of code
\cite{delayAndOrderLasecki,lessig2006code}.
This has spurred an entire body of work investigating the effects of
ordering,
pacing,
interruptions, and
other factors in piecework that would have been
all but impossible to measure consistently as few as 20 years ago
\cite{cheng2015break,measuringCrowdsourcingCheng,embracingErrorKrishna}.

@@

Rather than fall into the trap that \citeauthor{irani2015cultural} warns of,
--- one which where crowd workers are rendered as
``modular, protocol--defined computational services'' ---
we may yield better results from crowd work if we think of workers as similar to
specialized, repurposable tools
\cite{irani2015cultural}.
\ali{feeling meh about this argument\dots}

@@

\subsubsubsection{\implication}
crowd work research today is on the right track to investigate pipelining and meta--task design.
That is, investigating better work discovery methods, producing tools for workers to make more informed decisions
\cite[see, for example,][]{turkopticon}.
It's not clear how much benefit there is in the further decomposition of work,
given that we've hit bottlenecks with the cognitive stresses of switching between tasks
as \citeauthor{delayAndOrderLasecki} highlight
\cite{delayAndOrderLasecki}.

### 2016-09-13 drafts/labor/flexibility.tex
lots of changes all over the place

\onlyinsubfile{
  % \balance{}
  \printbibliography
  % \clearpage
  % \nobalance{}
  }
  \endnotetext{
    \section{Flexibility notes}
    A number of researchers have identified
    worker attrition%
,     variability of worker performance%
,     and uncertainty about good versus bad--faith actors as open questions of crowdwork
    \cite{MaliciousCrowdworkersGadiraju,Ipeirotis:2010:QMA:1837885.1837906}.
    \ali{We can and should discuss the distinction between presumably ``bad faith'' workers
    \& workers who are merely responding in kind to bad requesters
    --- and the broader questions surrounding
    the roles that requesters as well as workers should play ---
    but let it suffice to say that
    requesters have been trying to understand and manage what appears to them as inconsistent work.
    Their ways of responding to that variance in work quality has largely involved
    making the work more flexible and resilient to work
    (although some work has gone into investigating the causes, rather than treating the symptoms)}

    Earlier we discussed \citeauthor{cheng2015break}'s work
    measuring the impact that interruption has on worker performance
    \cite{cheng2015break}.
    This work illustrates a broader sentiment in
    both the study and practice
    of crowdwork, that microtasks should be designed resiliently against the variability of workers%
,     fully exploiting the abstracted nature of each piece of work
    \cite{interruptionIqbal,delayAndOrderLasecki,vaish2014low}.
    That is to say, micro--tasks should be designed such that a single worker's poor performance%
,     or a good worker's sudden departure%
,     does not significantly impact the agenda of the work as a whole.
    While \citeauthor{cheng2015break} found costs with breaking tasks into smaller components
    in the form of higher cumulative time to complete
    (albeit much shorter real time to complete, owing to parallelization)%
,     \citeauthor{delayAndOrderLasecki} found that at least \textit{some} performance can be recouped by stringing 
    similar tasks together
    \cite[respectively]{cheng2015break,delayAndOrderLasecki}.

@@

    The work thus far seems to attempt to maximize the quality of work among workers through various means:
    \begin{inlinelist}
      \item Identifying ``bad'' workers (fraught with problems as this characterization is) \cite{MaliciousCrowdworkersGadiraju}%
,       \item Designing tasks with break points to facilitate the on--boarding and off--boarding that happens anyway \cite{cheng2015break}, and
      \item Expecting certain levels of attrition and incorrectness and using that variability to their advantage \cite{embracingErrorKrishna}
    \end{inlinelist}.

>>>>

\onlyinsubfile{
  % \balance{}
  \printbibliography
  % \clearpage
  % \nobalance{}
  }
  \endnotetext{
    \section{Flexibility notes}
    A number of researchers have identified
    worker attrition%
,     variability of worker performance%
,     and uncertainty about good versus bad--faith actors as open questions of crowd work
    \cite{MaliciouscrowdworkersGadiraju,Ipeirotis:2010:QMA:1837885.1837906}.
    \ali{We can and should discuss the distinction between presumably ``bad faith'' workers
    \& workers who are merely responding in kind to bad requesters
    --- and the broader questions surrounding
    the roles that requesters as well as workers should play ---
    but let it suffice to say that
    requesters have been trying to understand and manage what appears to them as inconsistent work.
    Their ways of responding to that variance in work quality has largely involved
    making the work more flexible and resilient to work
    (although some work has gone into investigating the causes, rather than treating the symptoms)}

    Earlier we discussed \citeauthor{cheng2015break}'s work
    measuring the impact that interruption has on worker performance
    \cite{cheng2015break}.
    This work illustrates a broader sentiment in
    both the study and practice
    of crowd work, that microtasks should be designed resiliently against the variability of workers%
,     fully exploiting the abstracted nature of each piece of work
    \cite{interruptionIqbal,delayAndOrderLasecki,vaish2014low}.
    That is to say, micro--tasks should be designed such that a single worker's poor performance%
,     or a good worker's sudden departure%
,     does not significantly impact the agenda of the work as a whole.
    While \citeauthor{cheng2015break} found costs with breaking tasks into smaller components
    in the form of higher cumulative time to complete
    (albeit much shorter real time to complete, owing to parallelization)%
,     \citeauthor{delayAndOrderLasecki} found that at least \textit{some} performance can be recouped by stringing 
    similar tasks together
    \cite[respectively]{cheng2015break,delayAndOrderLasecki}.

@@

    The work thus far seems to attempt to maximize the quality of work among workers through various means:
    \begin{inlinelist}
      \item Identifying ``bad'' workers (fraught with problems as this characterization is) \cite{MaliciouscrowdworkersGadiraju}%
,       \item Designing tasks with break points to facilitate the on--boarding and off--boarding that happens anyway \cite{cheng2015break}, and
      \item Expecting certain levels of attrition and incorrectness and using that variability to their advantage \cite{embracingErrorKrishna}
    \end{inlinelist}.

### 2016-09-13 drafts/labor/piecework_lit.tex
lots of changes all over the place

\makeatletter
\makeatother
\begin{document}
\section{A Review of Piecework}
\topic{The HCI community has used the term ``piecework'' to describe
myriad instantiations of on--demand labor%
, but this reference has generally been offered in passing.}
As this paper principally traces a relationship between
the historical piecework and the contemporary crowdwork
(or on--demand labor more generally)%
, this casual familiarity with piecework may prove insufficient.
We'll more carefully discuss piecework in this section in order
to inform the subsequent sections --- and indeed, the entire argument.
Specifically, we will
\begin{inlinelist}
  \item define ``piecework'' as researchers in the topic understood it;
  \item trace the rise of piecework at a very high level%
,         identifying key figures and ideas during this time; and finally
  \item look at the fall of piecework, such as it was%
,         considering in particular
        the factors that may have led to piecework's eventual demise
\end{inlinelist}.

@@

\topic{Piecework took a circuitous path in its rise to the mainstream%
% from the field into the home and finally into factories%
, each time finding additional ways to leverage the advantages of piecework.}
First applied to farm work, as
\citeauthor{hughRaynbirdTaskWork} and others illustrate%
, the practice remained relatively obscure until
it was brought to the textile industry
\cite{hughRaynbirdTaskWork}.
At the turn of the \nth{20} century%
, when \citeauthor{riisOtherSideLives} was documenting abhorrent working \& living conditions of pieceworkers in New York City%
, \citeauthor{norton1900textile} was providing substantive guidance on various wage regimes%
, describing piecework comprehensively
% ``The timeworkers' wages should be verified by the timekeeper's book.''
\cite{riisOtherSideLives,norton1900textile}.
Soon after,
we saw the application of piecework systems in textile mills on the realization that
``[pieceworkers in Italy] will work as many hours as it is possible for him to stand''
\cite{clark1908cotton}.
% By the turn of the \nth{20} century%
% , \citeauthor{riisOtherSideLives} 
% the poor working and living conditions that were pervasive in
% an increasingly industrial United States
% \cite{riisOtherSideLives}.
% By the turn of the \nth{20} century,
best practices regarding the measurement and management of
piecework rates, and of workers in the engineering industry,
were beginning to take shape
\cite{burton1899commercial}.

@@

\subsection{Why is piecework relevant to crowdwork?}
Using the definition of piecework that we came up with earlier, we argue that
crowdwork is fundamentally an instantiation of piecework, and
that we can more precisely anticipate the answers to the open research questions we discussed earlier.
We'll show that the dimensions of crowdwork that the broader HCI community has been studying
align with the history of piecework, and that this can greatly inform predictions about the future of crowd work.

>>>>

\makeatletter
\makeatother
\begin{document}
\section{A Review of Piecework}
\topic{The HCI community has used the term ``piecework'' to describe
myriad instantiations of on--demand labor%
, but this reference has generally been offered in passing.}
As this paper principally traces a relationship between
the historical piecework and the contemporary crowd work
(or on--demand labor more generally)%
, this casual familiarity with piecework may prove insufficient.
We'll more carefully discuss piecework in this section in order
to inform the subsequent sections --- and indeed, the entire argument.
Specifically, we will
\begin{inlinelist}
  \item define ``piecework'' as researchers in the topic understood it;
  \item trace the rise of piecework at a very high level%
,         identifying key figures and ideas during this time; and finally
  \item look at the fall of piecework, such as it was%
,         considering in particular
        the factors that may have led to piecework's eventual demise
\end{inlinelist}.

@@

\topic{Piecework took a circuitous path in its rise to the mainstream%
% from the field into the home and finally into factories%
, each time finding additional ways to leverage the advantages of piecework.}
First applied to farm work, as
\citeauthor{hughRaynbirdTaskWork} and others illustrate%
, the practice remained relatively obscure until
it was brought to the textile industry
\cite{hughRaynbirdTaskWork}.
At the turn of the \nth{20} century%
, when \citeauthor{riisOtherSideLives} was documenting abhorrent working \& living conditions of pieceworkers in New York City%
, \citeauthor{norton1900textile} was providing substantive guidance on various wage regimes%
, describing piecework comprehensively
% ``The timeworkers' wages should be verified by the timekeeper's book.''
\cite{riisOtherSideLives,norton1900textile}.
Soon after,
we saw the application of piecework systems in textile mills on the realization that
``[pieceworkers in Italy] will work as many hours as it is possible for him to stand''
\cite{clark1908cotton}.
% By the turn of the \nth{20} century%
% , \citeauthor{riisOtherSideLives} 
% the poor working and living conditions that were pervasive in
% an increasingly industrial United States
% \cite{riisOtherSideLives}.
% By the turn of the \nth{20} century,
Best practices regarding the measurement and management of
piecework rates, and of workers in the engineering industry,
were beginning to take shape
\cite{burton1899commercial}.

@@

\subsection{Why is piecework relevant to crowd work?}
Using the definition of piecework that we came up with earlier, we argue that
crowd work is fundamentally an instantiation of piecework, and
that we can more precisely anticipate the answers to the open research questions we discussed earlier.
We'll show that the dimensions of crowd work that the broader HCI community has been studying
align with the history of piecework, and that this can greatly inform predictions about the future of crowd work.
